Hydras \& Co.

### 2022-05-20 doc/large-sets-chapter.tex

\begin{remark}
Some notations (mainly names of fast-growing functions) of our development may differ slightly from the literature. Although this fact does not affect our proofs, we are preparing a future version where the names $F\_alpha$, $f\_alpha$, $H\_alpha$, etc., are fully consistent with the cited articles.

@@

Now, consider any natural number $k>0$ any ordinal $0<\alpha<\epsilon_0$.  We would like to compute
a number $l$ such that the interval $[k,l]$ is $\alpha$-mlarge. So, 
the standard battle starting with $\iota(\alpha)$ and the replication factor $k$ will end after $(l-k+1)$ steps.

@@

But we do not know how to fill the dots yet \dots{}   In the next section, we will 
use \coq{} to reason  about the \emph{specification} of \texttt{L},
prove properties of any function which satisfies this specification.
In Sect.~\ref{sect:L-equations}, we use the \texttt{coq-equations} plug-in
to define a function \texttt{L\_}, and prove its correctness w.r.t. its specification.

>>>>

\begin{remark}
Some notations (mainly names of fast-growing functions) of our development may differ slightly from the literature. Although this fact does not affect our proofs, we are preparing a future version where the names $F_\alpha$, $f_\alpha$, $H_\alpha$, etc., are fully consistent with the cited articles.

@@

Now, let us consider some natural number $k>0$ and an ordinal $0<\alpha<\epsilon_0$.  We would like to compute
a number $l$ such that the interval $[k,l]$ is $\alpha$-mlarge. So, 
the standard battle starting with $\iota(\alpha)$ and the replication factor $k$ will end after $(l-k+1)$ steps.

@@

But we do not know how to fill the dots yet \dots{}   In the next section, we will 
use \coq{} to reason  about the \emph{specification} of \texttt{L},
prove properties of any function which satisfies this specification.
In Sect.~\ref{sect:L-equations}, we use the \texttt{coq-equations} plug-in
to define  \texttt{L\_}, then prove its correctness w.r.t. its specification.
